---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gtar)
```

## Helpful Links for Starting Out with R

So, where do you start? You unfortunately have to install stuff. It isn't too much though. You basically need R (the language itself) and you really need RStudio (the IDE).

```{r r_and_rstudio}
open_url("https://cloud.r-project.org")
open_url("https://www.rstudio.com/products/rstudio/download/#download")
```

How is R... organized? This graphic gives some sort of overview.

```{r r_landscape}
open_image("the_r_landscape.pdf")
```

Data science is so hot right now. Let's learn all about it with the R for Data Science book:

```{r r4ds}
open_url("https://r4ds.had.co.nz")
```

Want help, like right now? Check out RStudio Community:

```{r rstudio_community}
open_url("https://community.rstudio.com")
```

Let's talk some R on Twitter! Use the `#rstats` hashtag:

```{r twitter_rstats}
open_url("https://twitter.com/hashtag/rstats")
```


