---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gtar)
library(gt)
library(tidyverse)
```

## The **gt** Package! Making Tables Full of Data 

So, where do you start?

With any new R package, where do you first go for help?

- CRAN info page (link to vignette, maybe?)
- GitHub Repo (perhaps the README has some examples)
- pkgdown site (does it exist?)
- ???

**gt** is only available at GitHub (think of it as alpha software). Here's a link:

```{r gt_github}
open_url("https://github.com/rstudio/gt")
```

There is a link to a dedicated site! It's at the top of the page. In there, resources galore!

```{r gt_pkgdown}
open_url("https://gt.rstudio.com/")
```

First things to know:

- the main function in **gt** is: `<function name>()`
- Give `gt()` a data table <what kind of objects?>
- C'mon, use the pipe (`%>%`)!




Do we know some datasets we could use?

```{r datasets}
# <fill in dataset names here>
```




There are also datasets in **gt**. And they are...

```{gt datasets}
# <get some gt datasets>

# Which is the smallest, best for examples? Let's see it, by itself and gt-ified
```




Let's look at the pkgdown site again, and go to the Reference section (great place for seeing all the functions and examples).

```{r gt_reference_page_in_pkgdown_website}
open_url("https://gt.rstudio.com/reference/index.html")
```




What do you notice about the function names in that page? I'm talking about the three sections with a healthy smattering of functions each? <Answer Here>

```{r families_of_functions}
# Autocomplete in RStudio; let's really look at this and marvel at the utility...

# 

# 

# 
```




Let's take one of the gt datasets and make a table, something that'll fit on a page of paper. We'll start small but we will keep adding stuff until we get something real deluxe.

Vote on a dataset:

```{r}
dplyr::tribble(
  ~dataset_name, ~votes,
  "countrypops", 1,
  "sza",         5,
  "gtcars",      7,
  "sp500",       2,
  "pizzaplace",  6,
  "exibble",     5,
) %>%
  gt() %>%
  tab_style(
    style = cells_styles(bkgd_color = "gold"),
    locations = cells_data(
      columns = TRUE,
      rows = votes == max(votes)
    )
  ) %>%
  tab_header(
    title = md("The *Results* of the Vote!"),
    subtitle = md("At this **Meetup**, everyone has voice...")
  ) %>%
  cols_label(
    dataset_name = "Dataset",
    votes = "Votes"
  ) %>%
  tab_options(
    table.width = 550,
    table.font.size = 26,
    column_labels.font.size = 26
  ) %>%
  tab_footnote(
    footnote = md(
      paste0(
        "This dataset lost *really* badly. Kinda sad. ",
        emo::ji("sad")
      )
    ),
    locations = cells_data(
      columns = vars(dataset_name),
      rows = votes == min(votes)
    )
  )
```




```{r gt_based_on_gt_dataset}
#<gt dataset> %>%
#  <preprocessing> %>%
#  <gt stuff>
```

