---
title: "Toronto Open Data"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

http://bit.ly/opendatatoronto-demo

# Toronto Open Data

https://open.toronto.ca/

Data around Toronto's population, infrastructure, services, etc.

Let's read in the data...

```{r read_data}
# <find the data and read it in>
```

# `opendatatoronto`

There is a growing demand for open data and increased momentum in Toronto's civic spaces.

Demand for more data and more functionality.

https://sharlagelfand.github.io/opendatatoronto/

```{r install_opendatatoronto}
# install.packages("devtools") # if you don't have devtools
# devtools::install_github("sharlagelfand/opendatatoronto")
```

## Look at the data set

In the portal, data sets are called packages. Yes I know.

```{r show_package}
library(opendatatoronto)

# <show the package metadata>
```

The actual datasets are called resources:

```{r show_resources}
# <show the resurces available in the package>
```

## Get the data

You can get the resource directly in R, without having to download it first!

```{r}
apartments <- # <get the resource directly into R>
```

## Clean the data

The data's variable names are annoying to work with.

```{r clean_data}
library(janitor)

apartments <- apartments %>%
  # <function for cleaning the data's names>
```

Missing values are "N/A", not NA

Tedious to do it one by one...

```{r clean_data_part_2}
library(dplyr)

apartments %>%
  mutate(balcony_guards = ifelse(balcony_guards == "N/A", NA, balcony_guards),
         confirmed_storeys = ifelse(confirmed_storeys == "N/A", NA, confirmed_storeys))
```

```{r clean_data_part_3}
library(naniar)

apartments <- apartments %>%
  # <function to replace all "N/A" to NA!>
```

I know I want to look at data over time, so let's clean the year built variable too!

```{r clean_year_built}
apartments <- apartments %>%
  # <convert the year to numeric>
```

Let's look at how many years of data there are:

```{r year_built_histogram}
library(ggplot2)

# <histogram of year built>
```

Let's just look at 1900 onwards.

```{r data_after_1900}
apartments_built_after_1900 <- apartments %>%
  # <filter to include 1900 onwards only>
```

## Plot year built versus number of storeys

Has the number of storeys in an apartment building increased over time?

```{r year_built_vs_storys}
# <plot of year built versus number of storeys>
```

Ok, that's a lot of information. Let's look by decade instead!

```{r add_decade}
# <code to get decade>
```

Plot number of storeys by decade built instead

```{r}
# <plot number of storeys by decade>
```

Can't see all the points! Make them visible.

```{r}
# <code to make all data visible>
```

Take a sad plot and make it better!

```{r}
# <show labels for all decades>
# <clean up axis labels, add title, add data source)
# <add theme>
# <add colour?>
# <make text visible on screen?>
```

Please let me know if you have any issues!

https://github.com/sharlagelfand/opendatatoronto/issues